Optimal analysis of Discrete-time Time-Invariant Affine Systems

### 2018-10-08 paper.tex
derniere version

We will need the following notation :
\[
\ks:=\inf\left\{k\in\nn\mid \min\left\{\sup_{x\in\xin} x^\intercal Q x , \sup_{x\in\xin} x^\intercal (A^k)^\intercal Q A^k x+q^\intercal A^k x\right\}>0\right\}
\]
and
\[
\lfrak:= \min\left\{\sup_{x\in\xin} x^\intercal Q x , \sup_{x\in\xin} x^\intercal (A^{\ks})^\intercal Q A^{\ks}k x+q^\intercal A^{\ks}x\right\}
\]

@@

In the computations of the two integers, we need first a matrix that satisfies the discrete Lyapunov equation. For the computation of $K(1,P)$, we need $P \in \lyaun$. We propose to compute this matrix $P$ as an optimal solution  of the semi-definite problem:
\begin{equation}
\label{eq:kunp}
\begin{array}{llc}
\Min & &\lmax{P}\\
 & \st &\left\{\begin{array}{l} 
         P-Q\succeq 0\\
         P-A^\intercal P A-\varepsilon Id\succeq 0\\
         P\succeq  0
        \end{array}\right.
\end{array}
\end{equation}
where $\varepsilon$ is set to $0.001$.

For the computation of $K(\lmax{P^{-1/2}QP^{-1/2}},P)$, we need an element of $\lyap{A}$. We then solve the semi-definite problem:
\begin{equation}
\label{eq:klmaxp}
\begin{array}{llc}
\Min & &\lmax{P}\\
 & \st &\left\{\begin{array}{l} 
         P-A^\intercal P A-\varepsilon Id\succeq 0\\
         P\succeq  0
        \end{array}\right.
\end{array}
\end{equation}
where $\varepsilon$ is still set to $0.001$.
We will write $P_1$ for an optimal solution of Pb.~\eqref{eq:kunp} and $\pmax$ for an optimal solution of Pb.~\eqref{eq:klmaxp}.

@@

\subsubsection{Homogeneous objective function}
We consider the discretisation of an harmonic oscillator by Euler scheme. We want to prove that $x_{1,k}^2$ and $x_{1,k}^2$ are less than 1.

\subsubsection{Non-Homogeneous objective function}
We consider a property set of the form $C=\{x\in\rd\mid c^\intercal x\leq \beta,\ c^\intercal x\leq \alpha \}$ with $\alpha\leq \beta$. The latter $C$ can be rewritten as $\{x\in\rd\mid (c^\intercal x)^2-(\beta+\alpha) c^\intercal x\leq -\alpha\beta\}$. Assumption~\eqref{assumR} is true if and only $\alpha\beta< 0$ and thus only valid if $\alpha<0$.

@@

Rotation plus translation 
\subsubsection{Non-Homogeneous objective function}

>>>>

\ForAuthors{Compare with zero in the interior of xin... if 0 belongs to the interior of xin then we can choose xeps=epsilon sign(q) in xin and then q.xeps >0 and xeps Q xeps nonnegative...}

\ForAuthors{Q cannot be null indeed for all k the value would be negative or null}

\ForAuthors{From double linear inequalities i.e. alpha<=cx<= beta, we can cast into a quadratic inequality. However if the scalar part is not negative alpha*beta, we cannot use our method. }  
We will need the following notation :
\[
\ks:=\inf\left\{k\in\nn\mid \min\left\{\sup_{x\in\xin} x^\intercal Q x , \sup_{x\in\xin} x^\intercal (A^k)^\intercal Q A^k x+q^\intercal A^k x\right\}>0\right\}
\]
and
\[
\lfrak:= \min\left\{\sup_{x\in\xin} x^\intercal Q x , \sup_{x\in\xin} x^\intercal (A^{\ks})^\intercal Q A^{\ks}k x+q^\intercal A^{\ks}x\right\}
\]

@@

In the computations of the two integers, we need first a matrix that satisfies the discrete Lyapunov equation. For the computation of $K(1,P)$, we need $P \in \lyaun$. We propose to compute this matrix $P$ as an optimal solution  of the semi-definite problem:
\begin{equation}
\label{eq:kunp}
\begin{array}{llc}
\Min & &\lmax{P}\\
 & \st &\left\{\begin{array}{l} 
         P-Q\succeq 0\\
         P-A^\intercal P A-\varepsilon Id\succeq 0\\
         P\succeq  0
        \end{array}\right.
\end{array}
\end{equation}
where $\varepsilon$ is set to $0.01$.

For the computation of $K(\lmax{P^{-1/2}QP^{-1/2}},P)$, we need an element of $\lyap{A}$. We then solve the semi-definite problem:
\begin{equation}
\label{eq:klmaxp}
\begin{array}{llc}
\Min & &\lmax{P}\\
 & \st &\left\{\begin{array}{l} 
         P-A^\intercal P A-\varepsilon Id\succeq 0\\
         P\succeq  0
        \end{array}\right.
\end{array}
\end{equation}
where $\varepsilon$ is still set to $0.01$.
We will write $P_1$ for an optimal solution of Pb.~\eqref{eq:kunp} and $\pmax$ for an optimal solution of Pb.~\eqref{eq:klmaxp}.

@@

\subsubsection{Homogeneous objective function}
\label{exp-linear}
We consider the discretisation of an harmonic oscillator $\ddot{x}+\dot{x}+x=0$ by an explicit Euler scheme. The discretization step $h$ is set to 0.01. Introducing the position variable, $x$ and the speed variable $v$. We assume that the initial conditions can be taken into the set $[-1,1]^2$. The Euler scheme becomes a linear discrete-time system in dimension two defined as follows: 
\[
\begin{pmatrix}
x_{k+1}\\
v_{k+1}
\end{pmatrix}
=\begin{pmatrix}
1 & h\\
-h & 1-h
\end{pmatrix}
\begin{pmatrix}
x_{k}\\
v_{k}
\end{pmatrix},\ (x_0,v_0)\in [-1,1]^2
\]
We want to prove that for all $k\in\nn$, $x_{k}^2$ and $v_{k}^2$ are less than 1.

\subsubsection{Non-Homogeneous objective function}
We consider a property set of the form $C=\{x\in\rd\mid c^\intercal x\leq \beta,\ c^\intercal x\leq \alpha \}$ with $\alpha\leq \beta$. The latter $C$ can be rewritten as $\{x\in\rd\mid (c^\intercal x)^2-(\beta+\alpha) c^\intercal x\leq -\alpha\beta\}$. Assumption~\eqref{assumR} is true if and only $\alpha\beta< 0$ and thus only valid if $\alpha<0$. A MIEUX EXPLIQUER

Let us consider the same linear system as in Subsubsection~\ref{exp-linear}. We are interested in proving that for all $k\in\nn$, $-1\leq x_k-0.5v_k\leq 2$. This is the same as proving 
$(x_k-0.5 v_k)^2-x_k+0.5 v_k\leq 1$.
\subsection{Affine systems}

@@

Rotation plus translation

We propose to use the same linear system proposed by Ahmadi et al governed by a rotation transformation except we add a translation in the geometric transformation. For record, their system is governed by the rotation matrix:

\[
 \dfrac{4}{5}\begin{pmatrix}
 \cos(\theta)& sin(\theta)\\
-sin(\theta) & \cos(\theta)
\end{pmatrix},\text{ where }\theta=\dfrac{\pi}{6}
\]
We add a translation tranformation characterized by the vector $(1,-1)^\intercal$. 
We get the system:
\[
\begin{pmatrix}
x_{k+1}\\
y_{k+1}
\end{pmatrix}
= \dfrac{4}{5}\begin{pmatrix}
 \cos(\theta)& sin(\theta)\\
-sin(\theta) & \cos(\theta)
\end{pmatrix}
\begin{pmatrix}
x_{k}\\
y_{k}
\end{pmatrix}+\begin{pmatrix}
1\\
-1
\end{pmatrix},\ (x_0,y_0)\in [-1,2]^2
\]

We want to prove that for all $k\in\nn$, $x_k^2\leq 9$ and $y_k^2\leq 9$.
\subsubsection{Non-Homogeneous objective function}
